### 2010-03-18 papers/icfp-2010-desc/paper_idesc.tex
Desc@ICFP: Single column figures, where possible.
Desc@ICFP: point-wise sum.

Consequently, replacing $\Val{ty}$ by $(\SUM{\Val{ty}}{\Var{dom}{ty}})$ in
Figure~\ref{fig:hexpr-full} turns the language of closed term into a
language of opened terms with constants. \note{Is it polite and
  comprehensible to ask that?} This defines a new indexed description,
called $\HExprVarD{dom}$.

@@

\[
\begin{array}{@{}ll}
\substH  : & \PITEL{\V{\domNat}}{\EnumU} 
             \PITEL{\V{\gammaNat}}{\spi{\domNat}{(\LAM{\_} \IMu{\Ty}{\toIDesc{\HExprVarD{\domNat}}}{\Enat})}} \\
           & \PITEL{\V{\domBool}}{\EnumU} 
             \PITEL{\V{\gammaBool}}{\spi{\domBool}{(\LAM{\_} \IMu{\Ty}{\toIDesc{\HExprVarD{\domBool}}}{\Ebool})}} \\
          &  \begin{array}{@{}ll}
             \PI{\V{\sigma}}{& \PITEL{\V{\domNat}}{\EnumU} \\
                             & \PITEL{\V{\gammaNat}}
                                     {\spi{\domNat}{(\LAM{\_} \IMu{\Ty}{\toIDesc{\HExprVarD{\domNat}}}{\Enat})}} \\
                             & \PITEL{\V{\domBool}}{\EnumU} \\
                             & \PITEL{\V{\gammaBool}}
                                     {\spi{\domBool}{(\LAM{\_} \IMu{\Ty}{\toIDesc{\HExprVarD{\domBool}}}{\Ebool})}} \\
                             & \PI{\V{ty}}{\Ty} (\Val{ty} + \Var{dom_{ty}}{ty}) \To
                               \IMu{\Ty}{(\toIDesc{\HExprD})}{ty}}
             \end{array}\\
          & \PI{\V{ty}}{\Ty}
            \IMu{\Ty}{\toIDesc{\HExprVarD{dom_{ty}}}}{\V{ty}} \To
            \IMu{\Ty}{\toIDesc{\HExprD}}{\V{ty}}
\end{array}
\]

@@

The resulting data-type is called $\HExprFreeD$. By a simple unfolding
of definition, we note that $\FreeIMonad{\HExprFreeD}{\Ty}{\Val{}}$
corresponds to the syntax of closed terms, $\HExprD$. Similarly,
$$\FreeIMonad{\HExprFreeD}{\Ty}{(\LAM{ty} \Val{ty} + \Var{dom}{ty})}$$
corresponds to expressions with variables, $\HExprVarD{dom}$.

@@

\[\stk{
\substH\: \domNat\: \domBool\: 
            \gammaNat\: \gammaBool\:
            \sigma\: 
            ty\: 
            term \mapsto  \\
\;\;\ \begin{array}{ll}
       \substI\: & \Ty\: 
                  (\Val{} + \Var{dom_{ty}}{})\: 
                  \Val{}\:
                  \HExprFreeD\:  \\
                &
                  (\sigma\: \domNat\: \domBool\: \gammaNat\: \gammaBool)\:
                  ty\:
                  term
      \end{array}
}\]

>>>>

Consequently, replacing $\Val{ty}$ by
$(\SUM{\Val{ty}}{\Var{dom}{ty}})$ in Figure~\ref{fig:hexpr-full} turns
the language of closed term into a language of opened terms with
constants. For readability, we will abbreviate $\LAM{ty}
\SUM{\Val{ty}{\Var{dom}{ty}}}$ into $\SUM{\Val{}}{\Var{}{}}$ \note{Is
  it polite and comprehensible to ask that?} This defines a new
indexed description, called $\HExprVarD{dom}$.

@@

\[
\begin{array}{@{}ll}
\substH  : & \PITEL{\V{\domNat}}{\EnumU} 
             \PITEL{\V{\gammaNat}}{\spi{\domNat}{(\LAM{\_} \IMu{\Ty}{\toIDesc{\HExprVarD{\domNat}}}{\Enat})}} \\
           & \PITEL{\V{\domBool}}{\EnumU} 
             \PITEL{\V{\gammaBool}}{\spi{\domBool}{(\LAM{\_} \IMu{\Ty}{\toIDesc{\HExprVarD{\domBool}}}{\Ebool})}} \\
          &  \begin{array}{@{}ll}
             \PI{\V{\sigma}}{& \PITEL{\V{\domNat}}{\EnumU} \\
                             & \PITEL{\V{\gammaNat}}
                                     {\spi{\domNat}{(\LAM{\_} \IMu{\Ty}{\toIDesc{\HExprVarD{\domNat}}}{\Enat})}} \\
                             & \PITEL{\V{\domBool}}{\EnumU} \\
                             & \PITEL{\V{\gammaBool}}
                                     {\spi{\domBool}{(\LAM{\_} \IMu{\Ty}{\toIDesc{\HExprVarD{\domBool}}}{\Ebool})}} \\
                             & \PI{\V{ty}}{\Ty} (\SUM{\Val{ty}}{\Var{dom_{ty}}{ty}}) \To
                               \IMu{\Ty}{(\toIDesc{\HExprD})}{ty}}
             \end{array}\\
          & \PI{\V{ty}}{\Ty}
            \IMu{\Ty}{\toIDesc{\HExprVarD{dom_{ty}}}}{\V{ty}} \To
            \IMu{\Ty}{\toIDesc{\HExprD}}{\V{ty}}
\end{array}
\]

@@

The resulting data-type is called $\HExprFreeD$. By a simple unfolding
of definition, we note that $\FreeIMonad{\HExprFreeD}{\Ty}{\Val{}}$
corresponds to the syntax of closed terms, $\HExprD$. Similarly,
$$\FreeIMonad{\HExprFreeD}{\Ty}{(\LAM{ty} \SUM{\Val{ty}}{\Var{dom}{ty}})}$$
corresponds to expressions with variables, $\HExprVarD{dom}$.

@@

\[\stk{
\substH\: \domNat\: \domBool\: 
            \gammaNat\: \gammaBool\:
            \sigma\: 
            ty\: 
            term \mapsto  \\
\;\;\ \begin{array}{ll}
       \substI\: & \Ty\: 
                  (\SUM{\Val{}}{\Var{dom_{ty}}{}})\: 
                  \Val{}\:
                  \HExprFreeD\:  \\
                &
                  (\sigma\: \domNat\: \domBool\: \gammaNat\: \gammaBool)\:
                  ty\:
                  term
      \end{array}
}\]
